---
title: "week4"
author: "Chetan Narkhede"
date: "05/11/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## mtcars dataset


There is a set of variables related to MPG {outcome}.

Here the diff. of the MPG b/w auto & manual transmission is focused, 
the `mtcars` dataset in car package is taken as the data source, 
and techniques about regression models is used to solve the following two questions:

* “Is an auto or manual transmission better for MPG?”
*  “Quantifyingg how diifferent iis thee MilesPerGallon b/w auto & manual transmissions?”



## mtcars dataset - Format

**A data frame with 32 observations on 11 variables.**

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r cache=TRUE}
library(datasets)
mpgData <- with(mtcars, data.frame(mpg, am))
mpgData$am <- factor(mpgData$am, labels = c("Auto", "Man"))
#summary(mpgData)
```
## Motor Trend Car Road Tests


```{r cache=TRUE}
summary(mpgData[mpgData$am == "Auto",])
summary(mpgData[mpgData$am == "Man",])
```



```{r cache=TRUE}
fit <- lm(mpg ~ as.integer(am), data=mpgData)
summary(fit)
```
## Analysis - main code

Therefore, manual trans. is more efficient than auto for Miles_Per_Gallon, which increased by `r coef(fit)[2]`.

```{r cache=TRUE}
par(mfrow=c(1,2))
with(mpgData,{
     boxplot(mpg ~ am, 
             ylab = "miles per gallon (MPG)")
     plot(mpg ~ as.integer(am),
             xlab = "Auto (1) or Man(2)",
             ylab = "miles per gallon (MPG)")
     abline(fit, col=2)
     })
```


